---
title: "Vector used by frma for microarrays of type rat2302"
author: "Vincenzo Belcastro, Sylvain Gubian"

package: rat2302rnentrezgfrmavecs
output:
    BiocStyle::html_document

vignette: >
    %\VignetteIndexEntry{Vector used by frma for microarrays of type rat2302}
    %\VignetteEngine{knitr::rmarkdown}
    %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>"
)
```
# Description

The rat2302rnentrezgfrmavecs package was built from the set of 1023 microarray 
samples, distributed according to the table below. The maximum number of samples
per dataset is 93, and was selected to have a uniform sample distribution across
tissues (only 93 samples were available for the bone marrow tissue).

The table below reports the number of samples per dataset, for experiments
conducted on rat4302 affymetrics platform. The 93 samples per dataset were
selected as follow (steps applied for each dataset separately):

1. The official metadata file (e.g.: E-GEOD-XXXX.sdrf.txt) was loaded, and
    filtered to keep only those samples associated to the correct microarray
    platform;

2. A random uniform sampling (seed set to 4778) of 93 integer numbers (1 to
    number of samples of the dataset) were extracted 

3. The 93 rows of the metadata file were selected along with the corresponding
    samples;

4. The 93 samples (.CEL files) were extracted from the RAW data zip archives
    from ArrayExpress repository;

5. Once all 1023 (93 for each of the 11 tissues) samples were extracted the
    makeVectorPackage function was called with the batch.id parameter set to a
    vector of length 1023 (93 repetitions of each dataset names), and with
    annotation parameter set to rat2302cdf.

Step number 5 generates a package containing the vectors needed to the FRMA
tool, affy ID based in case the annotation parameter was set to rat2302cdf.

|                                   | Total  | Dataset      | Used     |
| ------:                           | :----- | ---------    | :------: |
| Adipose tissue                    | 101    | E-GEOD-13268 | 93       |
| Brain                             | 335    | E-GEOD-28435 | 93       |
| Eye                               | 120    | E-GEOD-5680  | 93       |
| Heart                             | 862    | E-GEOD-57800 | 93       |
| Kidney                            | 1410   | E-GEOD-57811 | 93       |
| Liver                             | 2218   | E-GEOD-57815 | 93       |
| Thigh muscle                      | 158    | E-GEOD-57816 | 93       |
| Bone marrow                       | 93     | E-GEOD-63902 | 93       |
| Mixed (testis/liver/brain/kidney) | 264    | E-MEXP-1568  | 93       |
| Bronchus                          | 164    | E-TABM-458   | 93       |
| Skeletal muscle                   | 126    | E-TABM-458   | 93       |
| **TOTAL**                         |        |              | **1023** |

# Basig usage

```{r, eval=TRUE, echo=TRUE, results='hide', message=FALSE, warning=FALSE}

library('affy')
library('frma')
library('rat2302rnentrezgfrmavecs')

celfile = system.file("extdata", "sample.CEL", 
                      package = "rat2302rnentrezgfrmavecs")
affybatch = ReadAffy(filenames = celfile, cdfname = 'rat2302rnentrezgcdf')
eset = frma(affybatch)

```
